---
title: "hw6_yj2579"
author: "Yingxi Ji"
date: "11/18/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
 echo = TRUE,
 fig.width = 8, 
 fig.height = 6,
 fig.asp = 0.6,
 out.width = "90%")
theme_set(theme_bw() + 
          theme(legend.position = "bottom",
                legend.title = element_blank(),
                plot.title = element_text(hjust = 0.5, size = 15),
                plot.subtitle = element_text(hjust = 0.5, size = 12)))

```

# Problem 1

## load the data
```{r}
birthweight = read_csv("./birthweight.csv") %>%
      janitor::clean_names() %>% 
    mutate(babysex = factor(babysex,level=c(1:2),
                    labels = c("male","female")),
           frace = factor(frace,level=c(1:4,8,9),
                    labels = c("White","Black",
                               "Asian","Puerto Rican",
                               "Other","Unknown")),
           malform = factor(malform,level=c(0:1),
                    labels = c("absent","present")),
           mrace = factor(mrace,level=c(1:4,8),
                    labels = c("White","Black",
                               "Asian","Puerto Rican",
                               "Other")))
```

## Checking NA
```{r}
sapply(birthweight, function(na) sum(is.na(na))) 
```

The `birth_weight` dataset consists of `r nrow(birthweight)` children and `r ncol(birthweight)` variables. The dataset does not have any NA.

## model buliding
```{r}
mod_select = lm(bwt ~ ., data = birthweight)
step(mod_select, direction = 'backward')
```

Using backward slection, I get a model: `bwt ~ babysex + bhead + blength + delwt + fincome +  gaweeks + mheight + mrace + parity + ppwt + smoken`

```{r}
mod1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
summary(mod1)
```

After checking the siginificance level of each explainitary variable, the final model fitted is: `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken` with an overall R-squared of 0.7181 which means my model captures 71.81% of variability and the p-value of overall F test being significantly less than 0.05. 


