---
title: "hw6_yj2579"
author: "Yingxi Ji"
date: "11/18/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)
library(ggplot2)
knitr::opts_chunk$set(
 echo = TRUE,
 fig.width = 8, 
 fig.height = 6,
 fig.asp = 0.6,
 out.width = "90%")
theme_set(theme_bw() + 
          theme(legend.position = "bottom",
                legend.title = element_blank(),
                plot.title = element_text(hjust = 0.5, size = 15),
                plot.subtitle = element_text(hjust = 0.5, size = 12)))

```

# Problem 1

## load the data
```{r}
birthweight = read_csv("./birthweight.csv") %>%
      janitor::clean_names() %>% 
    mutate(babysex = factor(babysex,level=c(1:2),
                    labels = c("male","female")),
           frace = factor(frace,level=c(1:4,8,9),
                    labels = c("White","Black",
                               "Asian","Puerto Rican",
                               "Other","Unknown")),
           malform = factor(malform,level=c(0:1),
                    labels = c("absent","present")),
           mrace = factor(mrace,level=c(1:4,8),
                    labels = c("White","Black",
                               "Asian","Puerto Rican",
                               "Other")))
```

## Checking NA
```{r}
sapply(birthweight, function(na) sum(is.na(na))) 
```

The `birth_weight` dataset consists of `r nrow(birthweight)` children and `r ncol(birthweight)` variables. The dataset does not have any NA.

## model buliding
```{r}
mod_select = lm(bwt ~ ., data = birthweight)
step(mod_select, direction = 'backward')
```

Using backward slection, I get a model: `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken`

```{r}
mod_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
summary(mod_fit)
```

After checking the siginificance level of each explainitary variable, the final model fitted is: `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken` with an overall R-squared of 0.7181 which means my model captures 71.81% of variability and the p-value of overall F test being significantly less than 0.05. 

## Model residuals against Fitted values
```{r}
birthweight %>% 
  add_predictions(model = mod_fit, var = "pred") %>% 
  add_residuals(model = mod_fit, var = "resid") %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.2, color = "2") +
  geom_smooth(se = F, color = "4") + 
  labs(title = "Model residuals against Fitted values", 
       y = "Residuals",
       x = "Fitted Value",
       caption = "Birthweight")
```

## Model comparing 
```{r}
set.seed(10)
# cv split
cv_birthw <- birthweight %>% 
  crossv_mc(10) %>% 
  mutate(
    train=map(train,as_tibble),
    test=map(test,as_tibble)
)
# compared two reference mods and my own model
cv_birthw <-  
  cv_birthw %>% 
  mutate(mod0  = map(train, ~lm(bwt ~ blength+gaweeks, data = .)),
         mod1  = map(train, ~lm(bwt ~ babysex*bhead*blength, data = .)),
         mod2  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .))
         ) %>% 
  mutate(rmse_mod0 = map2_dbl(mod0, test, ~rmse(model = .x, data = .y)),
         rmse_mod1 = map2_dbl(mod1, test, ~rmse(model = .x, data = .y)),
         rmse_mod2 = map2_dbl(mod2, test, ~rmse(model = .x, data = .y))
         ) 
  
# Keep CV results
cv_output <- cv_birthw[,c("rmse_mod0","rmse_mod1","rmse_mod2")]
sapply(cv_output,mean) 
```

Mod2 which is the our fitted model in the first part of the problem has the lowest rmse. Thus our model `bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken`has a best fit among those three models.


# Problem 2 
## Load the data
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

This is a dataset with `r nrow(weather_df)` observations and `r ncol(weather_df)` variables.

## SLR with tmax as the response and tmin as the predictor
```{r simple linear regression}
weather_slr = lm(tmax ~ tmin, data = weather_df)
summary(weather_slr)
```

we can get: $$\widehat{T_{max}} = 7.21 + 1.04*T_{min}$$

## R-squared and log(beta0*beta1) by bootstrap samples
```{r}
# function for bootstrap
DSbootstrap = function(x){
  mod_1 =
    x %>% 
    broom::tidy()
  
  mod_2 =
    x %>%
    broom::glance()
  
  tibble(
    r_squared = pull(mod_2, adj.r.squared),
    log_beta0_beta1 = log(pull(mod_1, estimate)[1] * pull(mod_1, estimate)[2]))
}

# Caculate the estimates for r_squared and log_beta0_beta1 using bootstrap samples
boot_straps = 
 weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, DSbootstrap)) %>% 
  unnest(results) %>%
  select(-strap, -models) 


boot_straps[1:6,] %>%
  rename("SLR model" = `.id`) %>%
  knitr::kable(align = 'c')

```

The table above showing the estimates of R-squared and log(beta0*beta1)

## R_squared
```{r}
boot_straps %>% 
  ggplot(aes(x = r_squared)) +
  geom_density(fill = "sky blue", alpha = .8, size = 2) +
  labs(title = "Distribution of R_squared", 
       x = "R_squared",
       y = "Density",
       caption = "Weather_df")

quantile(boot_straps$r_squared, c(.025, .975))
```

There is a little skewness but that is so small so we can ignore it and stick with this SLR.The left tail tells us that there may have more small values rather than large values. The 95% CI is (0.89347, 0.92683)

## log(beta0beta1)
```{r}
boot_straps %>% 
  ggplot(aes(x = log_beta0_beta1)) +
  geom_density(fill = "light yellow", alpha = .8, size = 2) +
  labs(title = "Distribution of log(beta0*beta1)", 
       x = "log(beta0*beta1)",
       y = "Density",
       caption = "Weather_df")
quantile(boot_straps$log_beta0_beta1, c(.025, .975))
```

The distribution is roughly normally distributed. We are 95% confident to say that the log(beta0beta1) will fall into the interval (1.966392, 2.057966).

